### 2019-05-24 doc/chapters/towards_verifying.tex
rewriting rype member

\subsection{Rewriting Generics}
Stainless output:
\begin{lstlisting}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]

@@

@@

>>>>

\subsection{Rewriting Generics}
// I dont understand this.. maybe just a missing feature in Stainless?
Stainless output:
\begin{lstlisting}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]

@@

\begin{lstlisting}
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

@@

\subsection{Rewriting Type Member}
Stainless output:
\begin{lstlisting}
  [Warning ] NumberType.scala:5:3: Could not extract tree in class: type A
             = BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
\end{lstlisting}
Since the type A is not overridden in any of its subclasses, this can simply be hard coded.
\begin{lstlisting}
  sealed abstract class Number {
    type A = BigInt
    protected def underlying: A
    def apply: A => T
  }
\end{lstlisting}
Replace every occurence of A with BigInt.
This might be a missing feature in Stainless that should not be to hard to fix.
There is an open issue on Github \mypound511.
